Activation-steering vectors for honesty raise truthfulness benchmarks, and this is widely read as evidence that the intervention moves an upstream concept. We ask whether the effect instead rides the model's output readout: a bias toward honest-coded words rather than a change in what the model computes. We separate the two by projecting a steering vector onto the orthogonal complement of the effective-unembedding rows (the unembedding composed with the RMSNorm Jacobian) for a chosen set of honesty-coded tokens. The projected vector has certified zero direct logit effect on those tokens, so any behavior it preserves must travel the indirect path through downstream layers; the preserved fraction $\rho$ measures depth. The statistic is only meaningful once two pitfalls are controlled. A steering magnitude must be selected under a coherence gate, because an over-large coefficient inflates teacher-forced multiple-choice scores while destroying free generation and turning $\rho$ into a ratio of noise; and the unembedding subspace must beat a random subspace of equal rank, or its removal proves nothing. On Llama-3-8B-Instruct we decompose two honesty-steering constructions head to head and find a double dissociation. The popular contrastive (CAA) vector shifts honesty-coded vocabulary by over a logit without improving truthfulness at any coherent strength; its apparent benchmark gain arises only after generation has collapsed (held-out perplexity \NaivePplRatio$\times$ baseline), where the naive analysis also reports a confident and meaningless $\rho \approx 1$. The mass-mean vector improves truthfulness at full coherence, with a test-set MC2 gain of \MmTestDelta, and its effect survives certified excision of its entire direct vocabulary readout: $\rho = \MmRhoAlSixtyFour$ \MmRhoAlSixtyFourCI, indistinguishable from random-subspace controls, stable from $k{=}16$ to $k{=}1024$ excised directions, and intact under paraphrase ($\rho_{\mathrm{OOD}} = \MmRhoOod$), while the logit lens shows downstream layers rebuilding the suppressed readout within two blocks. Where honesty steering works it is not vocabulary suppression, and where it is vocabulary-level it does not work. Code, token sets, certificates, and a formal proof of the construction are released.
