\begin{thebibliography}{20}

\bibitem[Arditi et~al.(2024)]{arditi2024refusal}
Andy Arditi, Oscar Obeso, Aaquib Syed, Daniel Paleka, Nina Panickssery, Wes Gurnee, and Neel Nanda.
\newblock Refusal in language models is mediated by a single direction.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2024.

\bibitem[Belrose et~al.(2023)]{belrose2023leace}
Nora Belrose, David Schneider-Joseph, Shauli Ravfogel, Ryan Cotterell, Edward Raff, and Stella Biderman.
\newblock {LEACE}: Perfect linear concept erasure in closed form.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2023.

\bibitem[Elhage et~al.(2021)]{elhage2021mathematical}
Nelson Elhage, Neel Nanda, Catherine Olsson, et~al.
\newblock A mathematical framework for transformer circuits.
\newblock \emph{Anthropic Technical Report}, 2021.

\bibitem[Grattafiori et~al.(2024)]{grattafiori2024llama3}
Aaron Grattafiori, Abhimanyu Dubey, Abhinav Jauhri, et~al.
\newblock The {Llama} 3 herd of models.
\newblock \emph{arXiv:2407.21783}, 2024.

\bibitem[Li et~al.(2023)]{li2023iti}
Kenneth Li, Oam Patel, Fernanda Vi\'egas, Hanspeter Pfister, and Martin Wattenberg.
\newblock Inference-time intervention: Eliciting truthful answers from a language model.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2023.

\bibitem[Lin et~al.(2022)]{lin2022truthfulqa}
Stephanie Lin, Jacob Hilton, and Owain Evans.
\newblock {TruthfulQA}: Measuring how models mimic human falsehoods.
\newblock In \emph{Proceedings of the 60th Annual Meeting of the Association for Computational Linguistics}, 2022.

\bibitem[Marks and Tegmark(2024)]{marks2024geometry}
Samuel Marks and Max Tegmark.
\newblock The geometry of truth: Emergent linear structure in large language model representations of true/false datasets.
\newblock In \emph{Conference on Language Modeling}, 2024.

\bibitem[Nadaf(2026)]{nadaf2026function}
Mohammed Suhail~B Nadaf.
\newblock Steerable but not decodable: Function vectors operate beyond the logit lens.
\newblock \emph{arXiv:2604.02608}, 2026.

\bibitem[nostalgebraist(2020)]{nostalgebraist2020logitlens}
nostalgebraist.
\newblock Interpreting {GPT}: The logit lens.
\newblock \emph{LessWrong}, 2020.

\bibitem[Park et~al.(2024)]{park2024linear}
Kiho Park, Yo~Joong Choe, and Victor Veitch.
\newblock The linear representation hypothesis and the geometry of large language models.
\newblock In \emph{Proceedings of the 41st International Conference on Machine Learning}, 2024.

\bibitem[Ravfogel et~al.(2020)]{ravfogel2020inlp}
Shauli Ravfogel, Yanai Elazar, Hila Gonen, Michael Twiton, and Yoav Goldberg.
\newblock Null it out: Guarding protected attributes by iterative nullspace projection.
\newblock In \emph{Proceedings of the 58th Annual Meeting of the Association for Computational Linguistics}, 2020.

\bibitem[Ravfogel et~al.(2022)]{ravfogel2022rlace}
Shauli Ravfogel, Michael Twiton, Yoav Goldberg, and Ryan Cotterell.
\newblock Linear adversarial concept erasure.
\newblock In \emph{Proceedings of the 39th International Conference on Machine Learning}, 2022.

\bibitem[Rimsky et~al.(2024)]{rimsky2024caa}
Nina Rimsky, Nick Gabrieli, Julian Schulz, Meg Tong, Evan Hubinger, and Alexander~Matt Turner.
\newblock Steering {Llama} 2 via contrastive activation addition.
\newblock In \emph{Proceedings of the 62nd Annual Meeting of the Association for Computational Linguistics}, 2024.

\bibitem[Tan et~al.(2024)]{tan2024analysing}
Daniel Tan, David Chanin, Aengus Lynch, Dimitrios Kanoulas, Brooks Paige, Adria Garriga-Alonso, and Robert Kirk.
\newblock Analysing the generalisation and reliability of steering vectors.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2024.

\bibitem[Taori et~al.(2023)]{taori2023alpaca}
Rohan Taori, Ishaan Gulrajani, Tianyi Zhang, Yann Dubois, Xuechen Li, Carlos Guestrin, Percy Liang, and Tatsunori~B. Hashimoto.
\newblock Stanford {Alpaca}: An instruction-following {LLaMA} model.
\newblock \url{https://github.com/tatsu-lab/stanford_alpaca}, 2023.

\bibitem[van Deventer(2024)]{hughvd2024benchmark}
Hugh van Deventer.
\newblock Unembedding-steering benchmark.
\newblock \url{https://github.com/hughvd/unembedding-steering-benchmark}, 2024.

\bibitem[Venkatesh and Kurapath(2026)]{venkatesh2026nonid}
Sohan Venkatesh and Ashish~Mahendran Kurapath.
\newblock On the non-identifiability of steering vectors in large language models.
\newblock \emph{arXiv:2602.06801}, 2026.

\bibitem[Zhang and Sennrich(2019)]{zhang2019rmsnorm}
Biao Zhang and Rico Sennrich.
\newblock Root mean square layer normalization.
\newblock In \emph{Advances in Neural Information Processing Systems}, 2019.

\bibitem[Zou et~al.(2023)]{zou2023repe}
Andy Zou, Long Phan, Sarah Chen, et~al.
\newblock Representation engineering: A top-down approach to {AI} transparency.
\newblock \emph{arXiv:2310.01405}, 2023.

\end{thebibliography}
