\section{Limitations}\label{sec:limitations}

Five limitations bound the claims. (1) \emph{One model.} All results are on Llama-3-8B-Instruct; the depth verdict could differ at other scales or families, and the apparatus is designed to be rerun (the RMSNorm correction applies to any modern pre-norm transformer). (2) \emph{First-order certificates.} The zero-direct-effect guarantee is exact for the linearized readout; the RMSNorm denominator makes the true map mildly nonlinear, and second-order leakage is bounded but not zero. The norm-matched control and the $k$-sweep both bound this concern empirically: if residual leakage carried the effect, $\rho$ would decay with $k$, and it does not. (3) \emph{Benchmark scope.} TruthfulQA MC is a narrow proxy for honesty, and its teacher-forced scoring is exactly the instrument we show to be gameable; we mitigate with the coherence gate, a held-out split, and paraphrase rescoring, but free-form honesty evaluation under steering remains open. (4) \emph{In-domain mass-mean supervision.} The mass-mean vector is built from TruthfulQA statements (disjoint questions from the test slice); its absolute effect size therefore benefits from distribution match, though the depth decomposition, which is the contribution here, is unaffected by where the vector came from. (5) \emph{Validation-selected operating points.} Operating points were chosen by validation gain, so the test-set effects shown here already include the resulting shrinkage (mass-mean: $\MmValDelta$ validation, $\MmTestDelta$ test); the CAA family shows what this protocol does when the validation gain was noise.
