Activation-steering vectors for honesty raise truthfulness benchmarks, and this is widely read as evidence that the intervention moves an upstream concept. We investigate whether the effect instead acts through the model's output readout, introducing a bias toward honest-coded words without altering the model's internal computation. We separate the two by projecting a steering vector onto the orthogonal complement of the effective-unembedding rows (the unembedding composed with the RMSNorm Jacobian) for a chosen set of honesty-coded tokens. The projected vector has certified zero direct logit effect on those tokens, so any behavior it preserves must travel the indirect path through downstream layers; the preserved fraction $\rho$ quantifies the depth of the effect. The statistic is meaningful only when two confounds are controlled. A steering magnitude must be selected under a coherence gate, because an over-large coefficient inflates teacher-forced multiple-choice scores while destroying free generation and rendering $\rho$ a ratio of noise; and the unembedding subspace must outperform a random subspace of equal rank, failing which its removal is uninformative. On Llama-3-8B-Instruct we decompose two honesty-steering constructions head to head and find a double dissociation. The widely used contrastive (CAA) vector shifts honesty-coded vocabulary by more than one logit without a material truthfulness gain at any coherent operating point; its apparent benchmark gain arises only after generation has collapsed (held-out perplexity \NaivePplRatio$\times$ baseline), a regime in which the naive analysis also reports a high but uninterpretable $\rho \approx 1$. The mass-mean vector improves truthfulness while staying within the coherence gate (held-out perplexity \MmPplRatio$\times$ baseline), with a test-set MC2 gain of \MmTestDelta, and its effect survives certified excision of its entire direct vocabulary readout: $\rho = \MmRhoAlSixtyFour$ \MmRhoAlSixtyFourCI, indistinguishable from random-subspace controls, never below \MmRhoKMin{} at any excision rank from $k{=}16$ to $k{=}1024$, intact under paraphrase ($\rho_{\mathrm{OOD}} = \MmRhoOod$), and confirmed in free-form generation judged by the unsteered model. Across four models (Llama-3, Mistral, Qwen2.5, and Llama-2) the CAA failure is universal, while the mass-mean effect replicates on three of the four (Llama-3, Mistral, and Llama-2) and is absent only on Qwen; wherever it is present, the majority survives readout excision ($\rho = \LlamaMmRho$, $\MistralMmRho$, and $\LlamaTwoMmRho$), indicating that the effect is carried predominantly by downstream computation rather than by vocabulary suppression. Code, token sets, certificates, and a formal proof of the construction are released.
