\section{Conclusion}\label{sec:conclusion}

We built the experiment that the vocabulary-suppression critique of honesty steering calls for: a token-conditional projection with machine-precision certificates that severs a steering vector's direct path to honesty-coded vocabulary, together with the two controls without which its statistic is uninterpretable, a coherence-gated operating point and a random-subspace baseline. Applied to two standard constructions, the test yields an unambiguous result. The contrastive CAA vector shifts honesty-coded vocabulary without improving truthfulness; its benchmark gains arise in a regime in which the model has ceased to produce coherent language, and an analysis that does not account for this regime yields a confident but uninterpretable depth verdict. The mass-mean vector improves truthfulness while staying within the coherence gate, and its effect survives complete excision of its vocabulary readout, remaining indistinguishable from random controls both in and out of distribution and in free-form generation. Across all four models the picture is consistent: the contrastive construction produces no material truthfulness gain, and the mass-mean effect, where it is present at all, is produced predominantly by the computations that downstream layers perform on the injected direction rather than by what the unembedding reads from it directly. The existence of the effect is itself model-dependent: it replicates on Mistral and Llama-2 but not on Qwen. What is robust across models is that vocabulary-level steering does not materially improve truthfulness, and that the truthfulness gains that do occur are not attributable to vocabulary suppression. The methodological controls that render those statements assertable, namely the coherence gate, the random-subspace control, and the certified projection, constitute a contribution equal in importance to the statements themselves.
