\section{Introduction}\label{sec:intro}

Activation steering has become a standard lever for controlling language-model behavior: add a contrastively constructed vector to the residual stream at a middle layer, and benchmark measures of honesty, refusal, or sentiment shift in the intended direction \citep{zou2023repe,rimsky2024caa,li2023iti,arditi2024refusal}. The appeal is mechanistic. The intervention appears to adjust a high-level concept that the model employs, and for honesty in particular this interpretation underwrites a safety argument: if a steering vector modifies an internal representation of truthfulness, the same vector should generalize across phrasings, domains, and languages.

But the same benchmark gain has a simpler explanation. A vector that merely shifts the output distribution toward words such as \emph{true} and \emph{honest} and away from \emph{lie} and \emph{deceive} could improve the score while altering nothing upstream. The two accounts---an upstream concept and a readout-level vocabulary bias---predict the same TruthfulQA score but very different out-of-distribution behavior. Standard evaluation cannot separate them, because an intervention at layer $\ell^{*}$ moves a shared residual that both the unembedding and the remaining transformer blocks consume.

We turn that ambiguity into an intervention. The first-order logit response to an injected vector $v$ splits into a direct term $\WUt^{*} v$, which the readout consumes unchanged, and an indirect term $\WUt^{*} M v$, which propagates through downstream attention and MLP blocks (Section~\ref{sec:method}). For a set $T$ of honesty-coded tokens, we project the steering vector onto the orthogonal complement of the corresponding rows of the \emph{effective} unembedding: the unembedding composed with the RMSNorm Jacobian at the readout point. Under the calibration-averaged effective unembedding, the projected vector $\vperp$ has zero first-order direct effect on every token in $T$, certified to machine precision, so any behavior it preserves must propagate along the indirect path. The preserved fraction, $\rho = \Delta(\vperp)/\Delta(\vdec)$, is therefore a depth statistic: it approaches $0$ when the effect was direct readout and $1$ when it was downstream computation.

That intervention alone is not enough. First, its denominator must be a genuine steering effect. We therefore select each vector's operating point under a coherence gate that rejects magnitudes which inflate held-out perplexity: a large coefficient can raise teacher-forced multiple-choice scores while degrading free generation to noise, leaving $\rho$ as a ratio of two noise terms. Second, the aligned unembedding subspace must be distinguished from a generic perturbation. We compare its removal with a random subspace of equal rank; if random projection eliminates the effect equally well, the effect was never concentrated in the readout and a high $\rho$ carries no readout-specific weight.

With these safeguards in place, the two steering constructions separate. On Llama-3-8B-Instruct, contrastive activation addition (CAA) strongly shifts honesty-coded vocabulary but yields no material truthfulness gain at any coherent operating point. The mass-mean direction does improve truthfulness (test-set $\Delta$MC2 of \MmTestDelta{} \MmTestDeltaCI), and that gain survives certified aligned-64 readout excision ($\rho = \MmRhoAlSixtyFour$ \MmRhoAlSixtyFourCI); in-domain, the loss is indistinguishable from random-subspace controls. The projected gain also survives paraphrase shift and free-form generation. The cross-model result sharpens rather than erases this dissociation: CAA fails on all four models, whereas mass-mean succeeds on Llama-3, Mistral, and Llama-2 but not Qwen; wherever the gain exists, most of it survives readout excision. Thus the existence of a useful steering effect is model-dependent, but its successful instances are predominantly downstream rather than vocabulary suppression.

\paragraph{Contributions.}
We make three contributions. (i) We introduce a token-conditional projection that zeroes a steering vector's direct logit contribution on a chosen token set, including the RMSNorm correction omitted by prior unembedding-orthogonal constructions, and provide machine-precision zero-direct-effect certificates. (ii) We pair the resulting depth statistic $\rho$ with a coherence-gated operating-point protocol and a random-projection control that make it interpretable. (iii) We apply the complete test head to head to CAA and mass-mean on Llama-3-8B-Instruct, then rerun it on Mistral-7B and Qwen2.5-7B from two other developers and Llama-2-7B from an earlier Llama generation. This establishes the double dissociation above: the CAA failure is universal, the mass-mean effect appears on three of four models, and wherever it appears the majority is carried downstream. All code, token lists, certificates, and the formal proof are available at \url{https://github.com/aryan-cs/liar-liar}.
