\section{Limitations}\label{sec:limitations}

Five limitations bound the claims. (1) \emph{Four models, one architecture class.} Results span Llama-3-8B, Mistral-7B, Qwen2.5-7B, and Llama-2-7B (Section~\ref{sec:multimodel}), all RMSNorm pre-norm transformers near 7--8B; behaviour at much larger scale, or under LayerNorm or logit-softcapping readouts (e.g.\ Gemma-2), is untested and would need the corresponding readout correction. The cross-model evidence itself shows the mass-mean \emph{effect} is model-dependent, so the depth verdict is reported only where that effect exists. (2) \emph{First-order certificates against an averaged readout.} The zero-direct-effect guarantee is exact for the linearized readout through the calibration-averaged Jacobian. Two approximations leave small but nonzero residual direct effects, both measured in Section~\ref{sec:method}: the per-point deviation of the Jacobian from its average leaves under $3\%$ of the unprojected vectors' median per-point direct effect, and the exact RMSNorm nonlinearity (all orders, not the first-order Jacobian) leaves at most \DecNonlinVperpMax{}/\MmNonlinVperpMax{} logits for CAA/mass-mean against unprojected direct effects of \DecNonlinVdecMax{}/\MmNonlinVdecMax{}, about $7\%$ and $4\%$ of the direct effect the projection removes respectively. The norm-matched control and the $k$-sweep provide a behavioral bound on any remaining residual: were the effect carried by residual leakage, $\rho$ would be expected to decay as $k$ grows, which is not observed. (3) \emph{Benchmark scope.} TruthfulQA MC is a narrow proxy for honesty, and its teacher-forced scoring is precisely the scoring instrument that we demonstrate to be susceptible to manipulation. We mitigate this with the coherence gate, a held-out split, and paraphrase rescoring; nevertheless, free-form honesty evaluation under steering remains an open problem. (4) \emph{In-domain mass-mean supervision.} The mass-mean vector is built from TruthfulQA statements (disjoint questions from the test slice); its absolute effect size therefore benefits from distribution match, although the depth decomposition, which constitutes the present contribution, is unaffected by the provenance of the vector. (5) \emph{Validation-selected operating points.} Operating points were chosen by validation gain, so the test-set effects shown here already include the resulting shrinkage (mass-mean: \MmValDelta{} validation, \MmTestDelta{} test); the CAA family illustrates the behavior of this protocol in the case where the validation gain was attributable to noise. The mass-mean operating point also sits at the boundary of the strength grid ($\alpha{=}4$ was the largest setting swept, and it remained coherent), so the reported effect size is the value selected by the protocol rather than necessarily the maximum attainable; in either case, the depth decomposition is computed at the selected operating point.
