\section{Related work}\label{sec:related}

Our question sits at the intersection of three literatures. Activation steering establishes the behavioral phenomenon, concept erasure supplies the form of intervention, and unembedding geometry identifies the readout path that must be removed. The closest precedents establish individual pieces of this test, but not the complete behavioral decomposition.

\paragraph{Activation steering.}
Representation engineering adds contrastively constructed vectors to the residual stream to modulate high-level behavior \citep{zou2023repe}. Contrastive activation addition \citep{rimsky2024caa} and inference-time intervention \citep{li2023iti} are the canonical honesty-adjacent instantiations, while \citet{arditi2024refusal} show that refusal is mediated by a single direction that can be removed from every writing matrix. Yet steering vectors often generalize poorly out of distribution \citep{tan2024analysing}, leaving open which part of the intervention carries the effect. Our depth statistic supplies a mechanism-level account of the conditions under which such failures are expected.

\paragraph{Concept erasure.}
To turn that ambiguity into an intervention, we draw on concept erasure. LEACE \citep{belrose2023leace} gives the minimum-norm affine map that removes linear decodability of a concept, following iterative nullspace projection \citep{ravfogel2020inlp} and rank-constrained adversarial erasure \citep{ravfogel2022rlace}. Our projection has the structure of LEACE with two changes: the erased subspace is read directly from the model's effective unembedding rather than learned from labels, and the constraint is zero direct logit contribution on a token set rather than zero probe accuracy.

\paragraph{Unembedding geometry.}
The relevant erased subspace comes from the duality between concept directions on the context and unembedding sides under a causal inner product, formalized by \citet{park2024linear}. Our rank-one variant projects against the unembedding-side honesty direction, and our Mahalanobis-weighted variant recovers their inner product. \citet{marks2024geometry} construct truth directions by mass-mean differences, which we use both as an alternative steering vector and as the readout-side direction of the rank-one test. The direct logit-attribution path through the residual stream follows the lens of \citet{elhage2021mathematical} and \citet{nostalgebraist2020logitlens}.

\paragraph{Closest precedents.}
Three works overlap most directly. \citet{venkatesh2026nonid} prove that steering vectors are non-identifiable up to perturbations in the null space of the full activation-to-logit Jacobian; our subspace is the readout-restricted version of their construction, and where they establish the existence of this ambiguity, we quantify its behavioral consequences. \citet{nadaf2026function} show that function vectors steer behavior the logit lens cannot decode, establishing the off-readout channel in the in-context-learning setting. The unembedding-steering benchmark of \citet{hughvd2024benchmark} implements $\WU$-orthogonal steering for sentiment on Gemma-2-9B. Together, these studies establish the ingredients of our test, but none applies the construction to honesty steering, corrects for the RMSNorm Jacobian, or reports a quantitative depth decomposition with certificates.
